---
title: ""
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes 
    toc: yes
    toc_float: yes
    code_folding: show
---


```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(kableExtra)
```

# Returns of financial stocks

We;re going to look at some NYSE data to help us make decisions on which stocks offer the best return for our risk.

```{r load_nyse_data, message=FALSE, warning=FALSE, echo=FALSE}
nyse <- read_csv(here::here("data","nyse.csv"))
```

```{r companies_per_sector, echo=FALSE}

nyse_comp_sect <- nyse %>% 
  group_by(sector) %>% 
  count(sort = TRUE)

nyse_comp_sect %>%
  kbl(col.names = gsub("[_]", " ", names(nyse_comp_sect))) %>%
  kable_material(c("striped", "hover")) %>%
  kable_styling(fixed_thead = T)

ggplot(nyse_comp_sect, aes(x = n, y = reorder(sector, n))) +
  labs(y = "Sector", x = "# of companies", title = "NYSE - Companies by sector") +
  geom_bar(stat='identity', show.legend = FALSE) + 
  geom_col() +
  theme_clean()

```


In the following section, we chose to download data for the following companies as well as the SP500 ETF:

* `GOOG`: Google
* `RY`: Royal Bank of Canada
* `AZN`: Astrazeneca
* `BP`: British Petroleum
* `DAL`: Delta Air Lines
* `TM`: Toyota
* `AMZN`: Amazon
* `SPY`: SP500 

```{r get_price_data, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}

myStocks <- c("GOOG","RY","AZN","BP","DAL","TM","AMZN","SPY") %>%
  tq_get(get  = "stock.prices",
         from = "2011-01-01",
         to   = "2020-08-31") %>%
  group_by(symbol) 

```

```{r calculate_returns, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
#calculate daily returns
myStocks_returns_daily <- myStocks %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "daily", 
               type       = "log",
               col_rename = "daily_returns",
               cols = c(nested.col))  

#calculate monthly  returns
myStocks_returns_monthly <- myStocks %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "monthly", 
               type       = "arithmetic",
               col_rename = "monthly_returns",
               cols = c(nested.col)) 

glimpse(myStocks_returns_monthly)

#calculate yearly returns
myStocks_returns_annual <- myStocks %>%
  group_by(symbol) %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "yearly", 
               type       = "arithmetic",
               col_rename = "yearly_returns",
               cols = c(nested.col))
```

## Monthly returns of stock portfolio and SP500

Here we calculate some summary statistics to help us evaluate these stocks.

```{r summarise_monthly_returns, echo=FALSE}

stock_returns_monthly <- myStocks_returns_monthly%>% 
  group_by(symbol) %>% 
  summarize(Min_return = min(monthly_returns), Max_return = max(monthly_returns), Median_return = median(monthly_returns), Mean_return = mean(monthly_returns), SD_return = sd(monthly_returns))
  
stock_returns_monthly %>%
  kbl(col.names = gsub("[_]", " ", names(stock_returns_monthly))) %>%
  kable_material(c("striped", "hover")) %>%
  kable_styling(fixed_thead = T)

```


```{r density_monthly_returns, echo=FALSE}

ggplot(myStocks_returns_monthly, aes(x=monthly_returns)) +
  geom_density(fill = "lightblue", alpha = 0.4) +
  labs(title = "Monthly returns of portfolio stocks (2011- 08/2020)", x = "Monthly returns", y = "Density") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 8)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 8)) + 
  facet_wrap(~symbol, scales='fixed') +
  theme_clean()

```

Looking at the plots of each stock, the Delta airlines stock is the riskiest as it has the highest volatility. As to be expected, the SP500 shows the lowest volatility compared to the chosen stocks as it tracks the average performance of all stocks in the respective index.

```{r risk_return_plot, echo=FALSE}

ggplot(stock_returns_monthly, aes(x = SD_return, y = Mean_return, colour = symbol)) +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = symbol)) +
  labs(title = "Expected monthly return of portfolio stocks",
       y = "Expected return (mean)", x = "Risk (standard deviation)") +
  theme_clean() +
  theme(legend.position = 'none')


```

The plot indicates that Amazon is clearly the stock with the strongest risk-reward profile in terms of expected return based on the mean monthly stock performance, followed by Google and Astra Zeneca. Looking at British Petroleum, the stock is underperforming in terms of risk-reward with a high standard deviation and an almost non-existent expected return.  
